\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
mention AM335x SoC

\subsubsection{Hardware}
\textit{BeagleBone Black}\cite{bbb} is selected as our major testing hardware platform powered by \textit{TI AM335x} \cite{am335x}, and it is an effective embedded platform, capable of running Linux and Xenomai (both 2 and 3), consisting of a single 1GHz ARM Cortex-A8 processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.

>>>>

\subsubsection{Hardware}
\textit{BeagleBone Black}\cite{bbb} is selected as our major testing hardware platform powered by \textit{TI AM335x} \cite{am335x} SoC, and it is an effective embedded platform, capable of running Linux and Xenomai (both 2 and 3), consisting of a single 1GHz ARM Cortex-A8 processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
